---
#Project Info
title: "BIOL432 Week3"
author: "Rain Zhu"
date: "29/01/2021"
link: https://github.com/JazzyRain/BIOL432
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)## used for knitting relating to output

```  
## Data Setup
```{r}

MyData<-read.csv("./InputData/FallopiaData.csv",header=T) #import data 
library(dplyr)#load dplyr
```
## Remove Data For Which the "Total" is less than 60 
```{r}
MyData<-MyData[!(MyData$Total<60),]## Exclude data of which the "Total" is < than 60
library(knitr)##load knitr
kable(MyData,caption="Fallopia Dataset")# show MyData
```
## Remove All Unnecessary Column, Leaving Total, Taxon, Scenario, Nutrient in the Respective Order
```{r}
MyData<-select(MyData, Total, Taxon, Scenario, Nutrients)##Select the dataframe MyData and only show Total, Taxon, Scenario and nutrients the variables are automatically arranged in order of code inputed
kable(MyData)# show MyData
```
## Convert Total(mg) ->Total(g)
```{r}
MyData$Total<-MyData$Total/1000#convert Total (mg) to Total (g) by dividing all Total(mg) by 1000
MyData<-rename(MyData,TotalG=Total)#rename the new Total(g) to TotalG
kable(MyData) # show MyData
```
## Using Custom Function to:
  1. Count the total number of observation in the Taxon Column 
  2. Calculate the average Total(g) for each of the 2 Nutrient concentrations
  
 Finally, save new data as "WrangledData.csv" in the Output folder 
```{r}

  source("./InputData/CustomFun.R")#Load custom function (CustomFun.R) from InputData 

MyData<-mutate(MyData,Number.of.Observation.in.Taxon=my.function(var1=MyData$Taxon,X="Observation"))
#make a new column with the mutate() function, within the column, we will use our custom function to determine the number of observation in Taxon


High<-MyData[(MyData$Nutrients=="high"),]## create new variable that represent all entries for high nutrients
Low<-MyData[(MyData$Nutrients=="low"),]## create new variable that represent all entries for low nutrients


MyData<-mutate(MyData,Average.TotalG.High.Nutrients=my.function(var1=High$TotalG,X="Average"))#use mutate() for new column, and use custom function along with High variable to input the average total(g) for high nutrients
MyData<-mutate(MyData,Average.TotalG.Low.Nutrients=my.function(var1=Low$TotalG,X="Average"))
#use mutate() for new column, and use custom function along with High variable to input the average total(g) for low nutrients
kable(MyData)# show MyData

write.csv(MyData,"./Output/WrangledData.csv")#save new csv file in the Output file

```
## Test Data For Error 

```{r}
is.na(MyData)# use is.na() to check for missing value; test for error 
```




